### 2022-01-02 doc/src/AdvPLIC.tex
Fix typo, in_setip -> in_clrip
Fix typo, "controoler" -> "controller"

\begin{commentary}
Because every {\RISCV} hart without an IMSIC has exactly one PLIC
as its external interrupt controoler, a system with multiple PLICs
must partition the harts into disjoint subsets, making each PLIC the
external interrupt controller for a separate subset of the harts.
While not prohibited, this arrangement is likely to be less efficient
than having all harts share a single PLIC.
\end{commentary}

@@

On a write to an \z{in\_clrip} register, for each bit that is one in
the \mbox{32-bit} value written, if that bit position corresponds to an
active interrupt source, the interrupt-pending bit for that source is
cleared if possible.
See Section~\ref{sec:AdvPLIC-pendingBits} for exactly when a pending
bit may be cleared by writing to an \z{in\_setip} register.

>>>>

\begin{commentary}
Because every {\RISCV} hart without an IMSIC has exactly one PLIC
as its external interrupt controller, a system with multiple PLICs
must partition the harts into disjoint subsets, making each PLIC the
external interrupt controller for a separate subset of the harts.
While not prohibited, this arrangement is likely to be less efficient
than having all harts share a single PLIC.
\end{commentary}

@@

On a write to an \z{in\_clrip} register, for each bit that is one in
the \mbox{32-bit} value written, if that bit position corresponds to an
active interrupt source, the interrupt-pending bit for that source is
cleared if possible.
See Section~\ref{sec:AdvPLIC-pendingBits} for exactly when a pending
bit may be cleared by writing to an \z{in\_clrip} register.
